%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{bm}
\begin{document}

\part{Apoorv Kumar}
	 {\fontfamily{phv}\selectfont\large Objective $\vert$ \fontfamily{cmr}\selectfont\large Work on high impact computer systems with steep growth of responsibilities and skills.}
     
\section{Work experience}

\begin{eventlist}

\item{October 2014 -- Present}
     {IMD Technology, Goldman Sachs}
     {Analyst, GSAM Data Platform}


Helped onboard and administer in memory \textit{MemSQL} which \textbf{reduced
the OTLP times} from minutes to sub-second. Developed a \textbf{secure auto-expiring token based authentication} on Kerberos V5 to access non-kerberized DBs. Developed \textbf{high throughput streaming} infra between \textit{Sybase IQ} and \textit{MemSQL}. Deployed \textit{Elastic Search} to \textbf{ingest raw legacy logs for search and visualization}. Developed \textbf{load balancing \& throttling algorithm} based on historical load stats using \textit{Apache Spark}. Algorithm reduced server crashes 10x.

\item{November 2013 -- October 2014}
     {IMD Strats, Goldman Sachs}
     {Analyst, Core Strat}

\textbf{First team member} in Bangalore with rest of the team spread across NY and London. \textbf{Grew the Bangalore unit to 5} over 2 years (larger than NY and London teams). Developed \textbf{light-weight event driven triggers} for data availability replacing old polling systems. \textbf{Improved data replication latency \& throughput} into HA clusters using native Sybase replication and transaction logs. Helped develop \textbf{DB agnostic high level language} over SQL for business logic.
Migrated team to IMD Tech.

\item{May 2013 -- September 2013}
     {IMD Strats, Goldman Sachs}
     {Analyst, Quant Strat}

Worked on \textbf{guidelines enforcement tool} for trades to follow regulatory/client guidelines for asset classes \& risk-return characteristics. Worked on \textbf{portfolio rebalancing \& trade planning tool} to improve prospective and retrospective analytics on trades. 


\end{eventlist}

\section{Internships}
\begin{eventlist}

\item{May 2012 -- July 2012}
     {Qualcomm India Pvt Ltd, Hyderabad}
     {Linux Platform Team}
Developed proprietary \textbf{Digital Video Broadcasting driver} (extension of Linux DVB) to leverage strengths of Qualcomm processors on Android. Analyzed microkernels to run on a low power microprocessor to \textbf{receive and decode multiplexed data streams} supporting process \& memory mgmt, IPC and IO.


\end{eventlist}


\personal
	[in.linkedin.com/in/apoorvkumart]
    {+91 7259211363}
    {apoorv.kumar247@gmail.com}

\section{Education}

\begin{yearlist}

\item[CBSE\newline Physics/Chem/Maths - 91\%]{2007 - 09}
     {Senior Secondary School}
     {DAV Kota, Rajasthan}

\item[Computer Science \& Engg \newline CGPA - 7.87/10]{2009 - 13}
     {Bachelor of Technology}
     {IIT Guwahati}

\end{yearlist}

\section{Publications}

\begin{yearlist}

\item{2014}
     {IEEE VLSI Design and Test 18th International Conference}
     {Modelling and analysis of wireless communication over Network-on-Chip}

\end{yearlist}

\section{Software skills}

\begin{factlist}

\item{Industry}
     {Java, Scala, SQL, Bash, Java Script, Apache Spark, Elastic Search, Apache Hadoop, Sybase IQ/ASE,  MySQL Cluster, MemSQL, Kerberos, Linux}

\item{Academic}
     {C, C++, Python, VLSI, SystemC}

\end{factlist}

\section{Achievements}

\begin{factlist}
\item{2009}{Rank 1376, IIT JEE}
\item{2011}{Rank 22, ACM ICPC Regional}
\item{2013}{Started IMD Core Strat team in Bangalore}
\end{factlist}


\section{Courses}

\begin{factlist}
\item{Maths}{Discrete Mathematics, Theory of Computation, Formal Languages}
\item{CS}{Operating Systems, Compilers, Databases, Distributed Computing, Wireless Networks, Communication networks, Compilers OOP, Software Engg., Advanced Computer Arch.}
\item{Econ.}{Macro Economics, Capital Markets, Algorithmic Game Theory, International Economics}
\end{factlist}

\end{document}
