%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%

\documentclass{tccv}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage{bm}
\usepackage[ampersand]{easylist}
\begin{document}

\part{Apoorv Kumar}
	 {\fontfamily{phv}\selectfont\large Objective $\vert$ \fontfamily{cmr}\selectfont\large Build and manage teams that deliver high impact computer systems.}
     
\section{Work experience}


\begin{eventlist}
\item{August 2017 -- Present}
	 {Shubh Loans}
	 {VP Technology \& Founding Team Member}
\textbf{Built the team} from 5 full-stack developers to 20 developers and data scientists with varying domains of expertise including analytics, data management, mobile/web apps, security and architecture.\newline
\textbf{Developed custom SDLCs} for different parts of infrastructure ranging from Agile to Waterfall depending on business speed/safety/visibility needs.
\textbf{Architected and lead the development} of a serverless+microservices based horizontally scalable and highly available lending platform that handles thousands of users per hour, millions of users overall and can automatically scale over 10x.\newline
\textbf{Platform is geared towards automating} the entire customer journey starting from customer acquisition (via our source integrations) to underwriting decisions (using an ML based proprietary decision framework) down to document generation and post disbursal collection support.\newline


\item{July 2016 -- July 2017}
     {IMD Technology, Goldman Sachs}
     {Associate, Trading Data Platform}
     We developed and managed a \textbf{real-time trade management system} with sub-100 microsecond response times using \textit{Apache Geode} and a distributed highly-available \textit{Java/Akka} application. \newline
     We built a \textbf{binary deployment system with configurable topologies} to compile binaries, manage configs and deploy clusters. Data was archived into a \textbf{HDFS/Sybase data-lake for reporting \& analytics} using \textit{Apache Spark \& Kafka}.


\item{May 2013 -- June 2016}
     {IMD Strategies, Goldman Sachs}
     {Analyst, Asset Management Data Platform}
	\textbf{Started and grew the Bangalore core-strat team} to 6 strong with recruits from IITs.\newline
	Helped develop \textbf{DB agnostic high level language} that compiled to DB specific SQL.\newline
	Deployed and managed distributed in-memory \textit{MemSQL} RDBMS and \textit{Elastic Search} clusters and developed \textbf{Kerberos based authentication and auto-expiring sessions} for them. \newline
	Developed \textbf{high throughput ETL infrastructure} between \textit{Sybase IQ} (analytics layer) and \textit{MemSQL} (presentation layer).\newline
	Developed \textbf{guidelines, portfolio rebalancing \& trade planning tool} to improve prospective and retrospective analytics on trades for Fixed Income desk.



\end{eventlist}



\personal
	[in.linkedin.com/in/apoorvkumart]
    {+91 7259211363}
    {apoorv.kumar247@gmail.com}

\section{Education}

\begin{yearlist}

\item[CBSE - 91\%]{2007 - 09}
     {Senior Secondary School}
     {DAV Kota, Rajasthan}

\item[Computer Science \& Engg \newline CGPA - 7.87/10]{2009 - 13}
     {Bachelor of Technology}
     {IIT Guwahati}

\end{yearlist}

\section{Milestones}

\begin{factlist}
	\item{2009}{Rank 1376, IIT JEE}
	\item{2011}{Rank 22, ACM ICPC Regional}
	\item{2013}{Started IMD Core Strategies team in Goldman Sachs Bangalore}
	\item{2015}{Grew IMD Core Strat Bangalore team to 6, largest among London/NY/Blr}
	\item{2017}{Head of engineering at Shubh Loans}
	\item{2019}{Shubh Loans tech team now \texttildelow20 strong}
\end{factlist}

\section{Publications}

\begin{yearlist}

\item{2014}
     {IEEE VLSI Design and Test 18th International Conference}
     {Modelling and analysis of wireless communication over Network-on-Chip}

\end{yearlist}

\section{Software skills}

\begin{factlist}

\item{Languages}
     {Java, Python, Java Script, Scala, SQL}

\item{Systems}
     {AWS - Redshift, EC2, S3, Lambda, Load Balancer, Batch\newline Apache - Spark, Hadoop, Geode \newline Databases- MySQL, Elastic Search, MongoDB, Sybase}

\item{Platforms}
	{Machine Learning - AWS Rekognition, Google Vision, Tensorflow, Scikit\newline
	Visualization - Airbnb Superset, Plotly Dash}
\end{factlist}



\end{document}
